Transfer Learning in Visual and Relational Reasoning

### 2020-02-06 Transfer_Learning/cvpr_2nd_submission/related_work.tex
motivation - in related work
Signed-off-by: ibm <tkornuta.ibm@gmail.com>

>>>>

\tk{The experimental results clearly indicate that transfer learning is helping, despite that the core assumptions on the compatibility/similarity of domains is broken (transfering between domains having similar distribution).
We do not understand this fully, thus the need for a more systematic research on that topic emerges.
The paper adresses that by introducing a theoretical framework/taxonomy enabling to categorise visual reasoning tasks. 
As a starting point, we picked two visual reasoning datasets and analyse the achieved results through the prism of the proposed taxonomy.
}
